A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-18 tex/body.tex
minor

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all theories. Overall, it accounts for a success rate
increase of \OK{5.2\%}. Moreover, every aspect of the procedure, including the
more expensive rules, make a contribution.
%* and finally, we look in more detail at one or two such proofs, by presenting
%  it and explaining it (and, before that, understanding it)
%
Three proofs were found thanks to
the \rn{Acyclic} rule and four required the \rn{Unique} rule. Among the latter,
three are one-line proofs in Isabelle, of the form
\keyw{by}~\textit{coinduction}~\textit{auto}\begin{rep} \cite{blanchette-et-al-2014-impl}\end{rep}.
The fourth proof, by Gammie and Lochbihler, is more elaborate:
%
\begin{quote}
\keyw{lemma} \,\textit{\nummodden\_unique}: \,$x = \const{Node}\;0\;\const{num}\; x \Longrightarrow x = \const{\nummodden}$ \\
\keyw{proof} \,(\textit{coinduction arbitrary}: $x$ \textit{rule}: \textit{tree.coinduct\_strong}) \\
\noindent\hbox{}\quad  \keyw{case} (\textit{Eq\_tree} $x$) \keyw{show} \textit{?case} \\
\noindent\hbox{}\qquad  \keyw{by} (\textit{subst} (1 2 3 4) \textit{Eq\_tree}) (\textit{simp add}: \textit{eqTrueI}[OF \textit{Eq\_tree}]) \\
\keyw{qed}
\end{quote}
%
\noindent
where \const{\nummodden} is defined as $\const{\nummodden} =
\const{Node}\;0\;\const{num}\;\const{\nummodden}$.

>>>>

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all theories. It accounts for an overall success rate
increase of over \OK{5\%}. Moreover, every aspect of the procedure, including the
more expensive rules, make a contribution.
%* and finally, we look in more detail at one or two such proofs, by presenting
%  it and explaining it (and, before that, understanding it)
%
Three proofs were found thanks to
the \rn{Acyclic} rule and four required the \rn{Unique} rule. Among the latter,
three are simple proofs of the form
\keyw{by}~\textit{coinduction}~\textit{auto} %\cite{blanchette-et-al-2014-impl}
in Isabelle.
The fourth proof, by Gammie and Lochbihler, is more elaborate:
%
\begin{quote}
\keyw{lemma} \,\textit{\nummodden\_unique}: \,$x = \const{Node}\;0\;\const{num}\; x \vthinspace\Longrightarrow\vthinspace x = \const{\nummodden}$ \\
\keyw{proof} \,(\textit{coinduction arbitrary}: $x$ \textit{rule}: \textit{tree.coinduct\_strong}) \\
\noindent\hbox{}\quad  \keyw{case} (\textit{Eq\_tree} $x$) \keyw{show} \textit{?case} \\
\noindent\hbox{}\qquad  \keyw{by} (\textit{subst} (1 2 3 4) \textit{Eq\_tree}) (\textit{simp add}: \textit{eqTrueI}[OF \textit{Eq\_tree}]) \\
\keyw{qed}
\end{quote}
%
\noindent
where \const{\nummodden} is defined as $\const{\nummodden} =
\const{Node}\;0\;\const{num}\;\const{\nummodden}$.
